gtsummary

### 2020-12-09 rmarkdown-gtsummary.Rmd
in progress

```{r}
tibble::tribble(
  ~Argument,       ~Description,
  "`label`",       "specify the variable labels printed in table",
  "`type`",        "specify the variable type (e.g. continuous, categorical, etc.)",
  "`statistic`",   "change the summary statistics presented",
  "`digits`",      "number of digits the summary statistics will be rounded to",
  "`missing`",     "whether to display a row with the number of missing observations",
  "`missing_text`","text label for the missing number row",
  "`sort`",        "change the sorting of categorical levels by frequency",
  "`percent`",     "print column, row, or cell percentages"
) %>%
  gt() %>%
  fmt_markdown(everything()) %>%
  as_latex() %>%
  as.character() %>%
  str_replace(fixed("\\toprule"), fixed("\\caption{\\label{tab:}\\texttt{tbl_summary()} function arguments}\\\\\n\\toprule")) %>%
  readr::write_lines("tbl_tbl_summary_args.tex")

@@

```{r}
tibble::tribble(
  ~Function,             ~Description,
  "`add_p()`",           "add p-values to the output comparing values across groups",   
  "`add_overall()`",     "add a column with overall summary statistics",   
  "`add_n()`",           "add a column with N (or N missing) for each variable",
  "`add_difference()`",  "add column for difference between two group, confidemce interval, and p-value",
  "`add_stat_label()`",  "add label for the summary statistics shown in each row",   
  "`add_stat()`",        "generic function to add a column with user-defined values",
  "`add_q()`",           "add a column of q values to control for multiple comparisons"   
)%>%
  gt(caption = "`tbl_summary()` functions to add information") %>%
  fmt_markdown(everything()) %>%
  fmt_markdown(everything()) %>%
  as_latex() %>%
  as.character() %>%
  str_replace(fixed("\\toprule"), fixed("\\caption{\\label{tab:}\\texttt{tbl_summary()} functions to add information}\\\\\n\\toprule")) %>%
  readr::write_lines("tbl_tbl_summary_family.tex")
```

>>>>

```{r}
tibble::tribble(
  ~Argument,       ~Description,
  "`label`",       "specify the variable labels printed in table",
  "`type`",        "specify the variable type (e.g. continuous, categorical, etc.)",
  "`statistic`",   "change the summary statistics presented",
  "`digits`",      "number of digits the summary statistics will be rounded to",
  "`missing`",     "whether to display a row with the number of missing observations",
  "`missing_text`","text label for the missing number row",
  "`sort`",        "change the sorting of categorical levels by frequency",
  "`percent`",     "print column, row, or cell percentages"
) %>%
  gt() %>%
  fmt_markdown(everything()) %>%
  as_latex() %>%
  as.character() %>%
  str_replace(fixed("\\toprule"), fixed("\\caption{\\label{tab:}\\texttt{tbl\\_summary()} function arguments}\\\\\n\\toprule")) %>%
  readr::write_lines("tbl_tbl_summary_args.tex")

@@

```{r}
tibble::tribble(
  ~Function,             ~Description,
  "`add_p()`",           "add p-values to the output comparing values across groups",   
  "`add_overall()`",     "add a column with overall summary statistics",   
  "`add_n()`",           "add a column with N (or N missing) for each variable",
  "`add_difference()`",  "add column for difference between two group, confidemce interval, and p-value",
  "`add_stat_label()`",  "add label for the summary statistics shown in each row",   
  "`add_stat()`",        "generic function to add a column with user-defined values",
  "`add_q()`",           "add a column of q values to control for multiple comparisons"   
)%>%
  gt(caption = "`tbl_summary()` functions to add information") %>%
  fmt_markdown(everything()) %>%
  fmt_markdown(everything()) %>%
  as_latex() %>%
  as.character() %>%
  str_replace(fixed("\\toprule"), fixed("\\caption{\\label{tab:}\\texttt{tbl\\_summary()} functions to add information}\\\\\n\\toprule")) %>%
  readr::write_lines("tbl_tbl_summary_family.tex")
```
